---
name: Anderson A.C.
surname: Alves
position: "Assistant Professor (Precision Livestock Science)"
address: "Department of Animal and Dairy Science, University of Georgia, 425 River Rd, Athens, GA, USA, 30602"
profilepic: "./img/profile.jpg"
www: "alvesand.netlify.app"
email: "alvesand@uga.edu"
github: alvesand
orcid: 0000-0001-8306-0487
headcolor: 414141
date: "`r format(Sys.time(), '%B %Y')`"
aboutme: "I work on the development and application of efficient statistical learning methods and computational tools for the analysis of large livestock data. My research program centers on combining on-farm sensor data and artificial intelligence (AI) techniques for animal monitoring. The general goal is to create decision-making tools that will support efficient management decisions. Additionally, we employ high-throughput phenotyping alongside modern molecular technologies to investigate the genetic basis of novel and hard-to-measure traits. Our lab mission is to harness top-notch technologies to improve animal production, reproduction, welfare and health, ultimately supporting efficient and sustainable livestock farming."
docname: CV
output: 
  vitae::awesomecv
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
library(dplyr)
library(here)
library(magrittr)
library(readr)
library(tidyverse)
library(kableExtra)
library(ggplot2)
library(scholar)

dire = getwd()
source("utils.R")

CV <- create_CV_object(
  data_location = "https://docs.google.com/spreadsheets/d/1Ef8qhBWs3hKk17O4mnHVio4fXTJeSmqzWW8W8UT79dU/edit?usp=sharing",  
  pdf_mode = FALSE
)

```

# EDUCATION

```{r}
CV$entries_data %>% 
  filter(section == 'education') %>% 
  detailed_entries(
    what = institution,
    when = glue::glue("{`start`} - {`end`}"),
    with = title,
    where = loc,
    why = description_bullets
  )
```

# PROFESSIONAL EXPERIENCE

```{r}
CV$entries_data %>% 
  filter(section == 'work') %>% 
  detailed_entries(
    what = institution,
    when = glue::glue("{`start`} - {`end`}"),
    with = title,
    where = loc,
    why = description_bullets
  )
```

# Research Interests

* Developing and applying computational and statistical tools for precision livestock farming and animal breeding.

* Integrating machine learning and sensor data for optimized livestock management.

* Leveraging modern molecular and sensor technologies to enhance farming efficiency and sustainability.


# PUBLICATIONS

\faicon{bar-chart-o} `r bibliography_entries("data/papers.bib") %>% filter(type == "article-journal") %>% summarize(N = n()) %>% pull(N)` **Refeered Journal Publications:**
```{r, results='asis'} 
authors_count <- count_authors("data/papers.bib")
cat("First author:", authors_count[1], ",", "Co-author:", authors_count[2], ",", "Corresponding author:", authors_count[3],"\n")
```

\faicon{book} `r bibliography_entries("data/book.bib") %>% summarize(N = n()) %>% pull(N)` **Book Chapters: **
```{r, results='asis'}
authors_count <- count_authors("data/book.bib")
cat("First author:", authors_count[1], ",", "Co-author:", authors_count[2], ",", "Corresponding author:", authors_count[3], "\n")
```

\faicon{file-text} `r bibliography_entries("data/paper_proc.bib") %>% summarize(N = n()) %>% pull(N)` **Conference Papers: **
```{r, results='asis'}
authors_count <- count_authors("data/paper_proc.bib")
cat("First author:", authors_count[1], ",", "Co-author:", authors_count[2], ",", "Corresponding author:", authors_count[3], "\n")
```

\faicon{users} `r bibliography_entries("data/abst.bib") %>% summarize(N = n()) %>% pull(N)` **Conference Abstracts: **
```{r, results='asis'}
authors_count <- count_authors("data/abst.bib")
cat("First author:", authors_count[1], ",", "Co-author:", authors_count[2], ",", "Corresponding author:", authors_count[3], "\n", "\n")
```

 
Full List Available at: https://alvesand.netlify.app/publications


```{r, results='asis', fig.width=5, fig.height=3, fig.align='center'}
id = "_JLXWlkAAAAJ&hl"
author <- scholar::get_profile(id)
cat("\n")

cat("Google Scholar statistics (", format(Sys.time(), '%B %Y'), "): ", " ")
cat("Citations: ", author$total_cites, ", h-index: ", author$h_index, " ,", "i10-index: ", author$i10_index,".",  "\n")
citations = get_citation_history(id)
citations = subset(citations, year>=2016)
cat("\n")
# Create a bar plot
ggplot(citations, aes(x = year, y = cites)) +
  geom_bar(stat = "identity", fill = "darkgrey") +
  labs(title = "",
       x = "Year",
       y = "Citations") +
  scale_x_continuous(breaks = unique(citations$year), expand = c(0, 0))
```

\begin{center}
\textbf{Figure 1.} Citation history since 2016. 
\end{center}



## **Peer-reviewed Papers**
```{r results='asis', fig.width=6, fig.height=4, fig.align='center'}
bibliography_entries("data/papers.bib") #%>%
  #arrange(desc(author$family), issued)
```
## 

## **Book Chapter**
```{r}
library(dplyr)
bibliography_entries("data/book.bib") #%>%
  #arrange(desc(author$family), issued)
```
##

## **Papers published in proceedings**
```{r}
library(dplyr)
bibliography_entries("data/paper_proc.bib") #%>%
  #arrange(desc(author$family), issued)
```
##

## **Conference Abstracts (*Last 3 years*)**
```{r}
library(dplyr)
bibliography_entries("data/recent_abs.bib")
```
## 

## **Forthcoming publications**
```{r}
library(dplyr)
bibliography_entries("data/ongoing.bib") #%>%
  #arrange(desc(author$family), issued)
```
##

# Grants

**Table 1.** Summary of grants awarded 
```{r, echo=FALSE, results='asis'}
data = read.csv(file = "data/grants.csv", sep = ",", h = T)
generate_latex_table(data, centered = F, pad = 0)
```

# Mentoring 

**Table 2.** Summary of mentoring activities 
```{r, echo=FALSE, results='asis'}
data = read.csv(file = "data/mentoring.csv", sep = ",", h = T)
generate_latex_table(data, centered = F, pad = 1)
```


# TEACHING
```{r}
CV$entries_data %>% 
  filter(section == 'teaching') %>% 
  detailed_entries(
    what = institution,
    when = glue::glue("{`start`}: {`end`}"),
    with = title,
    where = loc,
    why = description_bullets
  )
```



# Invited Presentations
```{r}
CV$entries_data %>% 
  filter(section == 'talk') %>% 
  detailed_entries(
    what = institution,
    when = glue::glue("{`start`} {`end`}"),
    with = title,
    where = loc,
    why = description_bullets
  )
```

# Software 

## R packages

* **qmtsvr**: (Quasi) Multi-task Support Vector Regression methods for genome-wide prediction of complex traits. **Documentation:** https://alvesand.netlify.app/qmtsvr_doc; **Source Code:** https://github.com/alvesand/qmtsvr  

## Python and R scripts

* **PyGA:** Runs a simple genetic algorithm for tuning hyperparameters in the sklearn library. **Source Code:** https://github.com/alvesand/pyga 

* **SISGlabs:** A suite of R scripts to illustrate some concepts in Quantitative Genetics and Mixed Model Theory. **Source Code:** https://github.com/alvesand/SISG_Labs_Modules_9_and_12 

# Service 

* **Ad-hoc Reviewer** - Journal of Animal Breeding and Genetics, BMC Genomics, Journal of Animal Science, Agriculture, Scientific Reports, Small Ruminant Research, Tropical Animal, Health and Production.

# Society Memberships 

* American Society of Animal Science (ASAS)

# Skills 

\begin{center}
\textbf{Table 3.} Highlighted technical skills. 
\end{center}

<!-- \noindent\makebox[\linewidth]{\rule{\textwidth}{0.4pt}} -->

<!-- \par\noindent\nobreak\vspace{-30pt}\rule{\textwidth}{1pt} -->

```{r techtable, results='markup'}
tribble(
   ~`Programming Languages`, ~`Analysis Tools`, ~`Expertise`,
  "R, Python, C++ (Beginner)",
  "Keras, Tensorflow,pytorch, scikit-learn, BLUPF90 suite programs, QMSim, Cytoscape, String, Genome Data Viewer,GS3",
  "Machine Learning, Big Data Analytics, Quantitative Genetics, Genomics, Computer Vision, Statistical Modelling, Simulation"
) %>%
  kable(booktabs = T, align = 'c', escape = F, format = "latex") %>%
  kable_styling(full_width = F, font_size = 9,latex_options = "hold_position") %>% 
  row_spec(0, bold = T, color = "#414141") %>% 
  row_spec(1, bold = F, color = "#7f7f7f") %>% 
  column_spec(column = 1:3, width = '4.75cm')
```

# Miscellaneous 

* **Languages:** English and Portuguese 
* **Place of birth:** Duque de Caxias, RJ, Brazil
* **DOB:** 01/14/1991

# References

References and additional information available upon request.
