---
name: Anderson A.C.
surname: Alves
position: "Assistant Professor (Precision Livestock Science)"
address: "Department of Animal and Dairy Science, University of Georgia, 425 River Rd, Athens, GA, USA, 30602"
profilepic: "./img/profile.jpg"
www: "alvesand.netlify.app"
email: "alvesand@uga.edu"
github: alvesand
orcid: 0000-0001-8306-0487
headcolor: 414141
date: "`r format(Sys.time(), '%B %Y')`"
aboutme: "I work on the development and application of efficient statistical learning methods and computational tools for the analysis of large livestock data. My research agenda center on combining on-farm sensor data and artificial intelligence (AI) techniques to create decision-making tools, supporting efficient and sustainable livestock farming"
docname: CV
output: 
  vitae::awesomecv
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
library(dplyr)
library(here)
library(magrittr)
library(readr)
library(tidyverse)
library(kableExtra)

dire = getwd()
source("utils.R")
source("count_authors.R")

CV <- create_CV_object(
  data_location = "https://docs.google.com/spreadsheets/d/1Ef8qhBWs3hKk17O4mnHVio4fXTJeSmqzWW8W8UT79dU/edit?usp=sharing",  
  pdf_mode = FALSE
)

```

# EDUCATION

```{r}
CV$entries_data %>% 
  filter(section == 'education') %>% 
  detailed_entries(
    what = institution,
    when = glue::glue("{`start`} - {`end`}"),
    with = title,
    where = loc,
    why = description_bullets
  )
```

# PROFESSIONAL EXPERIENCE

```{r}
CV$entries_data %>% 
  filter(section == 'work') %>% 
  detailed_entries(
    what = institution,
    when = glue::glue("{`start`} - {`end`}"),
    with = title,
    where = loc,
    why = description_bullets
  )
```


# PUBLICATIONS

\faicon{bar-chart-o} `r bibliography_entries("data/papers.bib") %>% filter(type == "article-journal") %>% summarize(N = n()) %>% pull(N)` **Refeered Journal Publications:**
```{r, results='asis'} 
authors_count <- count_authors("data/papers.bib")
cat("First author:", authors_count[1], ",", "Co-author:", authors_count[2], ",", "Corresponding author:", authors_count[3],"\n")
```


\faicon{book} `r bibliography_entries("data/book.bib") %>% summarize(N = n()) %>% pull(N)` **Book Chapters: **
```{r, results='asis'}
source("count_authors.R")
authors_count <- count_authors("data/book.bib")
cat("First author:", authors_count[1], ",", "Co-author:", authors_count[2], ",", "Corresponding author:", authors_count[3], "\n")
```

\faicon{file-text} `r bibliography_entries("data/paper_proc.bib") %>% summarize(N = n()) %>% pull(N)` **Conference Papers: **
```{r, results='asis'}
source("count_authors.R")
authors_count <- count_authors("data/paper_proc.bib")
cat("First author:", authors_count[1], ",", "Co-author:", authors_count[2], ",", "Corresponding author:", authors_count[3], "\n")
```

\faicon{users} `r bibliography_entries("data/abst.bib") %>% summarize(N = n()) %>% pull(N)` **Conference Abstracts: **
```{r, results='asis'}
source("count_authors.R")
authors_count <- count_authors("data/abst.bib")
cat("First author:", authors_count[1], ",", "Co-author:", authors_count[2], ",", "Corresponding author:", authors_count[3], "\n", "\n")
```

##
Full List Available on [Google Scholar](https://scholar.google.com/citations?view_op=list_works&hl=en&hl=en&user=_JLXWlkAAAAJ&pagesize=80&sortby=pubdate)
##

## **Peer-reviewed Papers**
```{r results='asis'}
bibliography_entries("data/papers.bib") #%>%
  #arrange(desc(author$family), issued)
```
## 

## **Book Chapter**
```{r}
library(dplyr)
bibliography_entries("data/book.bib") #%>%
  #arrange(desc(author$family), issued)
```
##

## **Papers published in proceedings**
```{r}
library(dplyr)
bibliography_entries("data/paper_proc.bib") #%>%
  #arrange(desc(author$family), issued)
```
##

## **Conference Abstracts (*Last 3 years*)**
```{r}
library(dplyr)
bibliography_entries("data/recent_abs.bib")
```
## 

## **Forthcoming publications**
```{r}
library(dplyr)
bibliography_entries("data/ongoing.bib") #%>%
  #arrange(desc(author$family), issued)
```
##

##

# TEACHING
```{r}
CV$entries_data %>% 
  filter(section == 'teaching') %>% 
  detailed_entries(
    what = institution,
    when = glue::glue("{`start`}: {`end`}"),
    with = title,
    where = loc,
    why = description_bullets
  )
```

# Mentoring 

```{r, echo=FALSE, results='asis'}
# Create a data frame with the specified items
data <- data.frame(
  Category = c("Undergraduate Research Projects (Advisor)", "Undergraduate Students (Committee member)", "Graduate Students (Co-advisor)", "Graduate Students Qualifying Exam (Committee member)"),
  Total = c("2", "3", "2", "2"),
  stringsAsFactors = FALSE
)

# Set the column widths
cw1 <- "12cm"  # Adjust the width as needed
cw2 <- "2cm"  # Adjust the width as needed

# Print the matrix with adjusted column widths and bold column names
cat("\\begin{tabular}{|p{", cw1, "} | p{", cw2, "} |}\n")
cat("\\hline\n")
cat("\\textbf{Category} & \\textbf{Total} \\\\\n")  # Bold column names
cat("\\hline\n")
cat(paste(data$Category, " & ", data$Total, " \\\\\n", sep = ""))
cat("\\hline\n")
cat("\\end{tabular}\n")
```




# Invited Presentations
```{r}
CV$entries_data %>% 
  filter(section == 'talk') %>% 
  detailed_entries(
    what = institution,
    when = glue::glue("{`start`} {`end`}"),
    with = title,
    where = loc,
    why = description_bullets
  )
```


# Service 
* Home automation 
* Beekeeping 
* Permaculture 
* Electronics design 
* Woodworking 

# Technical Skills 

<!-- \smallskip -->





# Conference Presentations


